%-------------------------
% Resume in Latex
% Author: Ubed Khan
% Based off of: https://github.com/sb2nov/resume
% License: MIT
%------------------------

\documentclass[a4paper,11pt]{article}
\pdfgentounicode=1

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.3in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Ubedurrehman Khan} \\ \vspace{1pt}
    \small \href{tel:+918657567454}{ \ +91 86575 67454} $|$ \href{mailto:kubedrn@gmail.com}{\underline{kubedrn@gmail.com}} $|$ 
    \href{https://linkedin.com/in/ubed9}{\underline{linkedin.com/in/ubed9}} $|$
    \href{https://github.com/ubednama}{\underline{github.com/ubednama}} $|$
    \href{https://ubednama.netlify.app/}{\underline{ubednama.netlify.app}}\\[4pt]
    Mumbai, IN
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \resumeSubheading
      {Mumbai University}{Navi Mumbai, MH}
      {Bachelor of Engineering in Computer Science}{Aug. 2019 - May 2023}
  \end{itemize}

%-----------PROGRAMMING SKILLS-----------
\noindent\section*{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Languages}{: JavaScript, Java, Python, C++, SQL} \\
     \textbf{Frameworks/Libraries}{: React.js, Node.js, Spring Boot, Kafka, RabbitMQ, RESTful API, gRPC, MVC, Jenkins} \\
     \textbf{Developer Tools}{: AWS, Git, Docker, CI/CD, Kubernetes, Redis}
    }}
 \end{itemize}

 \vspace{-7pt}

%-----------EXPERIENCE-----------
\section*{Experience}
    \begin{itemize}[leftmargin=0.15in, label={}]
        \resumeSubheading
          {Head of Department Intern, Web Development}{Oct 2023 - Present}{ADM Education Society}{Gurugram}
          \resumeItemListStart
            \resumeItem{Promoted to HOD and guided a team of 20 interns in developing the Maa Foundation website, enhancing user engagement and functionality.}
            \resumeItem{Introduced methodologies that increased productivity by 30\% and streamlined processes.}
            \resumeItem{Contributed to the ADM Education and Renu Health websites, delivering tailored solutions for various project needs, which helped accelerate website launch by 20\% and improved load time by 30\%.}
            \resumeItem{Oversaw deployment processes to ensure clean, scalable, and reliable software performance throughout the development lifecycle, resulting in a 50\% reduction in post-deployment issues.}
          \resumeItemListEnd
        
        \resumeSubheading
          {Full Stack Developer Intern}{Apr 2024 - May 2024}{Kothari Tech}{Mumbai}
          \resumeItemListStart
            \resumeItem{Led front-end development for Lofaz.in, an e-commerce platform, creating responsive user interfaces with React.js and CSS frameworks, which reduced page load time by 40\% and increased user retention by 20\%.}
            \resumeItem{Collaborated with UI/UX designers to translate design mockups into interactive components, aligning with project requirements and enhancing user interaction.}
          \resumeItemListEnd
    \end{itemize}


%-----------PROJECTS-----------
\noindent\section*{Projects}
    \begin{itemize}[leftmargin=0.15in, label={}]
    \resumeProjectHeading
        {\textbf{Expense Tracker} $|$ \emph{Java, Spring Boot, Kafka, MySQL}}{\href{https://github.com/ubednama/Expense-Tracker-Authservice}{\underline{GitHub}}}
            \resumeItemListStart
                \resumeItem{Built a Java-based scalable Expense Tracker with a microservices architecture using Spring Boot and Kafka, allowing users to track personal expenses in real-time.}
                \resumeItem{Designed an API Gateway for rate limiting and access control, integrated with AuthService for JWT generation, improving security and managing up to 5,000 simultaneous user sessions.}
                \resumeItem{Utilized ChatMistralAI’s LLM service for extracting transaction information from messages, automating data entry with 95\% accuracy and streamlining personal expense tracking.}
                \resumeItem{Developed a React Native mobile app, hosted backend services on AWS using Docker, and integrated email verification and reminder services, resulting in a 30\% increase in user engagement and satisfaction.}
            \resumeItemListEnd
        
    \resumeProjectHeading
      {\textbf{Flight Ticket Management System} $|$ \emph{Node.js, MySQL, AWS}}{\href{https://github.com/ubednama/Flights-Service} {\underline{GitHub}}}
      \resumeItemListStart
        \resumeItem{Engineered a flight ticket management system using Microservices Architecture, RabbitMQ, Sequelize, Node.js, Express.js, \& MySQL, optimizing real-time ticket display, booking, and management for high traffic efficiency.}
        \resumeItem{Designed a robust API Gateway system to handle over 10,000 incoming requests daily, enhancing system reliability and scalability by 50\%. Leveraged RabbitMQ for asynchronous service communication, improving system scalability and reducing coupling.}
        \resumeItem{Configured user Authentication and Authorization using JWT.}
      \resumeItemListEnd
      
  \resumeProjectHeading
      {\textbf{Project Management System} $|$ \emph{Spring Boot, React.js, MySQL, Tailwind, Razorpay}}{\href{https://github.com/ubednama/Project-Management-System}{\underline{GitHub}}}
      \resumeItemListStart
        \resumeItem{Architected a comprehensive project management system with JWT authentication and robust project tracking features, enabling real-time task management and user collaboration for over 1000 users and projects.}
        \resumeItem{Enabled secure and scalable payment processing with Razorpay integration for premium features and subscriptions, and devised OAuth for streamlined and secure user authentication, enhancing overall system security and user experience.}
      \resumeItemListEnd
\resumeProjectHeading
    {\textbf{Real-Time Chat App} $|$ \emph{Node.js, React.js, Socket.IO, MongoDB}}{\hfill \href{https://chat-app-uwfk.onrender.com/}{\underline{Link}} \textbar{} \href{https://github.com/ubednama/chat-app}{\underline{GitHub}}}
    \resumeItemListStart
        \resumeItem{Developed and deployed a real-time chat application using the MERN stack with Socket.IO, achieving over 99\% uptime and handling message delivery with less than 100ms latency.}
        \resumeItem{Configured JWT authentication for secure user sessions and optimized scalability, enhancing performance and reliability by 50\% under high-traffic conditions.}
    \resumeItemListEnd
    \end{itemize}

%-------------------------------------------
\vfill
\center{\footnotesize Last updated: \today}

\end{document}
